Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-10 fplc-elic.tex
thoughts on links

\begin{definition}
  Elicitation complexity of $\Gamma:\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
\end{definition}

@@

\begin{definition}
  Let $\gamma:\P\toto\R$.
  We say a property $\Gamma:\P\toto\reals^d$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \iff \varphi(r') \in \gamma(p)$.
\end{definition}
\raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}

>>>>

\begin{definition}
  Elicitation complexity of $\Gamma:\P\toto\R$... \raf{this is a guess...} min dimension of $\Gamma'\in\mathcal{C}\cap\mathcal{E}$ with either a selective or exhaustive link to $\Gamma$.
  \raf{Maybe break into ``selective'' and ``exhaustive'' versions?}
\end{definition}

@@

\begin{definition}
  Let $\Gamma:\P\toto\R$.
  We say a property $\Gamma':\P\toto\R'$ \emph{embeds $\gamma$} if \raf{we need to settle on this:} there is an injection $\varphi:\R\to\R'$ such that $r\in\Gamma(p) \iff \varphi(r) \in \Gamma'(p)$.
\end{definition}
\raf{Note: the above definition is general and not specific to FPLC, finite propertes, etc.}

\begin{proposition}
  If elicitable $\Gamma':\P\toto\R'$ embeds non-degenerate $\Gamma:\P\toto\R$, there is a selective link $f:\R'\to\R$ from $\Gamma'$ to $\Gamma$.
\end{proposition}
\begin{proof}
  Define $F:\R'\toto\R$ as follows: $F(r') = \bigcap\{\Gamma(p) : r'\in\Gamma'(p)\} = \bigcap\{\Gamma(p) : p \in\Gamma'_{r'}\}$.
  That is, $F$ encodes all reports of $\Gamma$ which could be correct when $r'$ is chosen from $\Gamma'$.
  \raf{Show $F(r') \neq \emptyset$ for all $r'$... we'll definitely need non-degeneracy here, and I think elicitability of $\Gamma'$ too.}
  We simply define $f$ to be any single-valued function such that $f(r') \in F(r')$ which satisfies $f(\varphi(r)) = r$ for all $r\in\R$.
  (This is a consistent choice by definition of $\varphi$.)

  It remains to show that $f$ is a selective link.
  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
  For (ii), let $p$ be given.
  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
  By (i), this must be an equality.
\end{proof}
